
\pdfpagewidth 8.5in
\pdfpageheight 11in
\pdfhorigin 1in
\pdfvorigin 1in

\nopagenumbers
\parindent=0pt

\font\rm=ptmr at 10pt
\font\bf=ptmb at 10pt
\font\it=ptmri at 10pt
\font\sl=ptmbo at 10pt
\font\tt=pcrr at 10pt
\font\tb=pcrb at 10pt
\font\zdb=pzdr at 10pt
\font\lgrm=ptmr at 24pt
\font\smrm=ptmr at 9pt
\font\superrm=ptmr at 8pt

\def\super#1{\lower -.5ex \hbox{\superrm #1}}
\def\xmrk{{\zdb 4}}

\rm

{\lgrm Christopher L.~Rorvick\hfill\vbox{\smrm
\hbox to 3in {\hfil
921 Canonero Drive\quad $\bullet$\quad Naperville, IL~~60540}
\hbox to 3in {\hfil
(630) 416-0382\quad $\bullet$\quad chris@rorvick.com}
}}

\vskip 5pt \hrule \vskip 10pt

\long\def\section#1#2{\leftskip 1in \noindent\llap{\hbox to 1in {\bf #1\hss}}{#2}\vskip 10pt}
\long\def\lastsection#1#2{\leftskip 1in \noindent\llap{\hbox to 1in {\bf #1\hss}}{#2}}
\long\def\subsection#1#2{{\sl #1}\hfill{\bf #2}}
\def\bulleted#1#2{\setbox0=\hbox{#1\ }\hangindent=\wd0#1 #2}


\section{PROFILE}{%
Software designer with fourteen years experience producing high quality
solutions across multiple industries using many technologies.
Eight years in the financial industry focusing on low-latency systems
and infrastructure supporting automated trading.
}

\section{EDUCATION}{%
{\bf University of Illinois}\quad Urbana--Champaign\par
\subsection{B.S.~in Computer Science}
    {May 2000}
}

\section{EXPERIENCE}{%
\parskip=5pt
{\bf Cognitive Capital, LLC}\quad Chicago, IL

Liquidity provider to capital markets using proprietary automated trading
technology.

\vskip 5pt
\subsection{Software Engineer}
    {April 2012 -- May 2014}

Member of core development team responsible for company's distributed
trading platform consisting of a hierarchy of multi-threaded C++
services.

\bulleted{$\bullet$}{%
Designed and implemented major overhaul of execution subsystem with
focus on improving signal attribution and coordination of various
execution components.  Design considerations included reducing thread
contention and improving cache efficiency.
}

\bulleted{$\bullet$}{%
Implemented new real-time signals as C++ services using specifications
from financial engineering.  Worked with portfolio managers on rollout
including facilitating rotational studies, data analysis, and
implementing reporting of nightly parameterization.
}

\bulleted{$\bullet$}{%
Contributed numerous improvements to C++ infrastructure to modernize API
and reduce boilerplate.
Identified opportunities for optimization through instrumentation and
profiling and measured system-wide impact using side-by-side testing
environment.
}

\bulleted{$\bullet$}{%
Planned and implemented migration of CVS repositories to Git.  Retooled
substantial legacy automation and designed integration process for
nightly build.  Prepared training material and led instructional
sessions
}

\bulleted{$\bullet$}{%
Designed and implemented automation using Perl to incorporate new
releases of the IANA (aka, Olson) Time Zone Database into the
Boost.Date\_Time format used for trading.
Updates are queued to development (leveraging Git ``plumbing'') for
validation and reported to the Operations Desk for vetting.
Process accommodates several deficiencies in Boost design.
}

\vskip 10pt

{\bf TradeLink, LLC}\quad Chicago, IL

Trading firm participating in a range of asset classes including
securities, futures, and options.

\vskip 5pt
\subsection{Software Designer, Algorithmic Trading \& Execution}
    {September 2010 -- February 2012}

Responsible for maintaining and deploying software for firm's two
algorithmic trading platforms and implementing and maintaining trading
strategies within these platforms.

\bulleted{$\bullet$}{%
Optimized trading of a \$40 million portfolio by migrating execution
logic from legacy Python platform to C++ smart order router.
Reduced latency by roughly four milliseconds per transaction.
}

\bulleted{$\bullet$}{%
Analyzed execution for a high frequency FX basis trade.
Automated reporting of time-series data pulled from disparate sources
into consolidated plots.
Recommended and implemented several optimizations included refactoring
the top-level execution logic, bug fixes to the feed handler, and
tuning the network stack.
}

\bulleted{$\bullet$}{%
Implemented FIX trading interface within firm's C++ trading platform
providing trading strategies with direct connectivity to exchanges.
}
\vfil\eject

\subsection{Software Designer / Technical Lead, Application Development}
    {January 2007 -- August 2010}

Developed and maintained many applications and infrastructure
components critical to the firm.
Managed development efforts including providing design and technical
direction to other developers.

\bulleted{$\bullet$}{%
Designed and implemented distribution framework for market data
via shared memory with C++ API.
Significantly reduced load on network infrastructure and trader
workstations allowing groups to participate and profit on high-volume
events that were previously not tradeable at the firm.
}

\bulleted{$\bullet$}{%
Managed a project to allow execution desk traders to monitor hundreds of
positions across the portfolios of its managed funds.  Included C++
libraries, server, and client application.
}

\bulleted{$\bullet$}{%
Maintained C++ screen trading application displaying a ``price ladder''
including aggregate book and trade volumes.  Supported click trading and
auto-spreads.
}

\bulleted{$\bullet$}{%
Implemented multi-threaded C++ feed handler for Eurex's
{\it New Socket Datafeed} providing non-netted, low-latency price data
to fixed income group operating in London office.
}

\vskip 5pt
\subsection{Software Developer, Application Development}
    {June 2005 -- June 2006}

Maintained a number of trading applications and back office software
critical to the day-to-day operations of the firm.

\bulleted{$\bullet$}{%
Enhanced and maintained a suite of C++ options trading applications
including two auto-traders and a program for monitoring implied
volatilities in real-time.
}

\bulleted{$\bullet$}{%
Responsible for maintaining firm's legacy Java platform including
post-trade and back-office applications.  
Automated build process and refactored code base into versioned
reusable modules.
}

\bulleted{$\bullet$}{%
One of two developers maintaining and providing 24x7 production support
for clearing system.
Implemented Python modules for processing semi-standard and
firm-specific data formats.
}

\vskip 10pt

{\bf Impact Forensics, LLC}\quad Chicago, IL

\subsection{Manager of Electronic Discovery}
    {July 2006 -- December 2006}

Managed lab for firm specializing in electronic discovery and expert
witness services including capacity planning and acquiring necessary
hardware.  Performed numerous on-site data acquisitions following
chain of custody procedures.

\vskip 10pt

{\bf U.S.~Cellular Corp.}\quad Bensenville, IL

\subsection{\sl Programmer / Systems Analyst}
    {February 2003 -- May 2005}

Worked on and lead development efforts in areas including account
management, billing, and business intelligence.  Representative on ATIS
committee responsible for standardizing local number portability between
wireless carriers.

\vskip 10pt

{\bf Universal Access, Inc.}\quad Chicago, IL

\subsection{\sl Senior Developer}
    {April 2001 -- April 2002}

Development lead on a team building a platform for automated pricing
and provisioning of long-haul telecommunication circuits using Java
J2EE technologies.

\vskip 10pt

{\bf Second Millennium Consulting, Inc.}\quad Chicago, IL

\subsection{Software Developer}
    {January 2000 -- March 2001}

Implemented solutions for clients of this startup consulting firm
specializing in Java J2EE and Oracle.  Worked in several industries
including media, marketing, and telecommunications.
}
\vfil\eject

\section{PUBLIC}{%
\parskip=3pt
\subsection{Git}        {\tb https://git.kernel.org/pub/scm/git/git.git}

\bulleted{$\bullet$}{%
Added support for per author time zones to {\tt cvsimport(1)} command.
Allows commit log timestamps to be associated with appropriate UTC
offsets.
}

\bulleted{$\bullet$}{%
References are generally allowed to update when pushing to a remote
repository if the new commit is a descendent of the old.  Added logic to
reject ``fast-forwarding'' a tag unless it is forced (e.g., with the
{\tt -{-}force} option.)
}

\bulleted{$\bullet$}{%
Various additions and updates to documentation.
}

\vskip 8pt

\subsection{CVSps}       {\tb https://git.gitorious.org/cvsps/cvsps.git}

Eric S.\ Raymond took over CVSps in late 2012 and added an option to
dump a CVS repository to a Git {\tt fast-import(1)} stream.  Tested
development tree for these changes and contributed numerous patches.

\vskip 8pt

\subsection{Hobson Village directory}
                      {\tb https://github.com/crorvick/hv-directory.git}

Automated generation of neighborhood directory saving many hours of
volunteer time annually.  Wrote a Perl script to convert CSV input data
into \TeX\ which is then used to generate PDF output ready for printing.
}

\section{SKILLS}{%
{\bf Programming:} C, C++, Perl, Python, Java

{\bf Scripting:} Bourne/Bash, Sed, AWK, Tcl, Autotools, Make, SQL

{\bf Version control:} Git, CVS, Subversion, SCCS

{\bf Databases:} PostgreSQL, Sybase, MySQL, Oracle

{\bf Data analysis:} R, gnuplot, Octave

{\bf Operating systems:} Redhat/Fedora Linux, Solaris, HP-UX

{\bf Libraries:} Boost, Intel TBB, pthreads, Armadillo, ACE, GTK+

{\bf Miscellaneous:} TCP/IP networking, GNU software, \TeX
}

\section{TRAINING}{%
\xmrk\quad Astoria Seminar, Extraordinary C++

\xmrk\quad Sun Certified Programmer for the Java 2 Platform

\xmrk\quad Application Development for WebSphere MQ 5.3

\xmrk\quad Application Development for Tuxedo 6.5

\xmrk\quad HP-UX Administration for Experienced UNIX Administrators

}

% Need to be smarter about how \section is defined so that the \vskip
% at the end doesn't cause an empty page.
\lastsection{OTHER}{%
Treasurer -- Hobson Village Community Association\hfill
2008 -- 2012\par

Board member -- Hobson Village Community Association\hfill
2006 -- 2008\par

Officer -- Triangle Fraternity, Alpha Chapter\hfill
1997 -- 1998

Eagle Scout -- Boy Scouts of America\hfill
1994%
}
\end
